\documentclass[12pt,a4paper,sans]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{carlito}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{microtype}
\usepackage[scale=0.85]{geometry}

% Personal data
\name{Berkay}{Vuran}
\title{Conversational Analytics Product Analysis Team Leader}
\address{Ankara, Türkiye}{}{}
\phone[mobile]{+90 542 423 99 30}
\email{berkaypsy@gmail.com}
\homepage{berkayvuran.com}
\social[linkedin]{berkay-vuran}

\begin{document}

\makecvtitle

% Professional Summary
\section{Summary}
\cvitem{}{Product professional with 7+ years of experience across AI, PropTech, telco, logistics, and enterprise software sectors. Specialized in product strategy, user experience design, and data-driven decision-making. Demonstrated success in leading cross-functional teams, driving digital transformation initiatives, and implementing ML/AI technologies. Proven track record in expanding operations to 230 countries, managing platforms serving 6M+ users, and improving key metrics including revenue growth (+150\%) and customer satisfaction. Holds PMP, Professional Scrum certifications (PSPO, PSM, PSU, PSD, PSFS, PSK), and Professional Agile Leadership credentials. Strong background in psychology and organizational behavior, combining technical expertise with deep understanding of user needs and team dynamics.}

% Experience
\section{Experience}

\cventry{12.2025--Present}{Conversational Analytics Product Analysis Team Leader}{SESTEK}{Ankara (Hybrid)}{}{
\begin{itemize}
\item Led strategic direction of Conversational Analytics Product Analysis team, defining analytical standards and aligning with product vision
\item Managed team performance end-to-end including objective setting, coaching, performance reviews, and competency development
\item Oversaw delivery quality across all product analysis outputs ensuring consistency, accuracy, and maintainability
\item Developed scalable analysis processes and best-practice guidelines for requirement elicitation and UX workflow design
\item Coordinated with Product Owners and engineering leaders to ensure requirements were clear and technically feasible
\item Conducted data-driven evaluations of product performance, identifying UX bottlenecks and improvement opportunities
\item Represented SESTEK in external events and C-level product reviews, contributing to thought leadership
\end{itemize}}

\medskip

\cventry{09.2024--12.2025}{Lead Product Analyst}{SESTEK}{Ankara (Hybrid)}{}{
\begin{itemize}
\item Conducted comprehensive product and market analyses including competitor research and literature reviews
\item Designed interfaces and workflows for new modules through mockups and diagrams defining requirements
\item Optimized product performance and UX by evaluating design efficiency, ensuring vision alignment
\item Served as liaison between development teams and Product Owners, facilitating communication
\item Directed product documentation ensuring details were captured and maintained for transparency
\item Delivered C-level presentations and represented SESTEK at industry events for thought leadership
\item Collaborated on sustainable product roadmaps while analyzing team efficiency to optimize workflows
\item Led design standardization, creating cohesive language as Subject Matter Expert for multiple teams
\item Provided training sessions and supported high-severity request resolution for timely responses
\end{itemize}}

\newpage

\cventry{11.2022--09.2024}{Senior Product Manager \& Scrum Master}{Emlakjet}{Istanbul (Remote)}{}{
\begin{itemize}
\item Catalyzed organization's Agile transformation, serving as Scrum Master and fostering continuous improvement culture
\item Spearheaded implementation of ML, NLP, and generative AI technologies in PropTech domain, driving product innovation
\item Contributed to CRO, ASO, and SEO optimization efforts while leading data-driven product development processes
\item Coordinated product development for Jettaşın (moving digitalization platform) from concept to launch
\item Streamlined automation of lead management and transfer processes, improving operational efficiency
\item Developed solutions to combat abuse and fraud on platform, enhancing security for B2B and B2C users
\end{itemize}}

\medskip

\cventry{01.2022--11.2022}{Product Owner}{Navlungo}{Istanbul (Remote)}{}{
\begin{itemize}
\item Managed four critical business domains (freight, payment, legal, and data), expanding customer base to 70,000+ users and facilitating 1,000,000+ transactions
\item Drove 150\% increase in sales and expanded operations to 230 countries across 3 continents
\item Led end-to-end development of deliver.ist (global ship \& shop service) from concept to launch in 3 months
\end{itemize}}

\medskip

\cventry{11.2021--01.2022}{Senior Business Analyst}{Etiya}{Ankara (Hybrid)}{}{
\begin{itemize}
\item Played key role in one of the five largest digital transformation projects in telco world, leading CRM transformation for Ooredoo, the largest telecom company in MENA region
\item Conducted comprehensive technical and non-technical HLD and LLD analyses using Jira and Confluence, ensuring clear documentation and seamless cross-team communication
\item Developed and implemented detailed UAT scenarios, effectively validating system functionality and ensuring alignment with business requirements
\item Led UX research and design efforts, ensuring user experience was intuitive and aligned with customer needs, contributing to higher adoption rates
\end{itemize}}

\medskip

\cventry{02.2019--11.2021}{Product Owner \& Business Analyst}{Ministry of Health, Republic of Türkiye}{Ankara}{}{
\begin{itemize}
\item Led UX research and interface design using Balsamiq and Figma, improving user satisfaction by 30\%
\item Architected and managed development of ALO184 SABİM platform serving 6,000,000+ users annually
\item Developed user cases and scenarios for Meeting Point Web Application, supporting 100,000 users annually and streamlining internal communication by 25\%
\item Directed technical and business analyses using Jira, TFS, and Confluence across 5+ national health programs, improving project efficiency by 30\%
\item Gathered and synthesized user requirements from over 50,000 healthcare professionals and patients
\end{itemize}}

% Key Achievements
\section{Key Achievements}

\cvitem{Revenue Growth}{Led product analytics and strategic initiatives at Navlungo that contributed to 150\% sales growth, expanding operations to 230 countries across 3 continents. Managed four critical business domains (freight, payment, legal, data) and facilitated 1,000,000+ transactions with 70,000+ active users.}

\medskip

\cvitem{Large-Scale Platform}{Architected and managed development of ALO184 SABİM platform serving 6,000,000+ users annually at Turkish Ministry of Health. Led UX research improving user satisfaction by 30\% and project efficiency by 30\%.}

\medskip

\cvitem{Team Leadership}{Established scalable product analysis framework and team leadership model at SESTEK. Led strategic direction of Product Analysis team, defining analytical standards, managing performance reviews, and developing team capabilities while improving delivery quality.}

\medskip

\cvitem{AI/ML Integration}{Successfully integrated ML/AI technologies including NLP-based property matching, generative AI, and machine learning solutions in PropTech domain at Emlakjet, driving product innovation and improving conversion rates through data-driven product development.}

\medskip

\cvitem{Rapid Execution}{Led end-to-end development of deliver.ist (global ship \& shop service) from concept to launch in just 3 months at Navlungo. Coordinated product development for Jettaşın (moving digitalization platform), delivering seamless user experiences.}

\medskip

\cvitem{Digital Transformation}{Played key role in one of the five largest digital transformation projects in telco world, leading CRM transformation for Ooredoo (largest telecom company in MENA region) at Etiya, ensuring smooth project rollout and higher adoption rates.}

\medskip

\cvitem{Agile Leadership}{Catalyzed organization's Agile transformation at Emlakjet, serving as Scrum Master and fostering continuous improvement culture. Managed all phases of SDLC ensuring timely delivery of high-quality products.}

% Education
\section{Education}
\cventry{2019--2024}{MSc, Organizational Behavior}{Hacettepe University}{}{GPA: 3.86/4.00}{}

\medskip

\cventry{2020--2022}{Associate Degree, Web Design \& Development}{Anadolu University}{}{GPA: 3.08/4.00}{}

\medskip

\cventry{2013--2017}{BSc, Psychology}{Hacettepe University}{}{GPA: 3.55/4.00}{}

% Skills
\section{Skills}
\cvitem{Product}{Product Strategy, Roadmap, Prioritization, A/B Testing, Customer Development}
\cvitem{Analytics}{AWS QuickSight, Google Analytics, SQL, Tableau, Power BI, Mixpanel, Amplitude}
\cvitem{Tools}{Jira, Confluence, Figma, Miro, Azure DevOps, Notion, Productboard}
\cvitem{Methodologies}{Agile, Scrum, Kanban, OKRs, Design Thinking, Lean Startup}
\cvitem{Technology}{API Integration, AWS, Machine Learning, NLP}

% References
\section{References}

\cventry{}{Erçin Altundağ}{Presales Manager, SESTEK}{}{}{}
\cvitem{}{``I had the opportunity to work with Berkay while serving as Presales Manager. One of the things that stood out most about Berkay was his excellent communication style---both within the team and across departments. He consistently approached every interaction with empathy and an open mind, always aiming to understand the person and the underlying need without bias. During presales engagements, I frequently gathered feedback and requirements from potential clients. Whenever I shared these insights with Berkay, he was not only receptive but also proactive in analyzing the input and exploring feasible solutions. His strong sense of empathy, combined with his ability to understand and dissect business needs, made him a valuable partner.''}

\medskip

\cventry{}{Özge Seçkin}{Team Lead, Emlakjet}{}{}{}
\cvitem{}{``I've had the pleasure of working with Berkay for the past 2 years as his team leader. Berkay excels at managing multiple projects simultaneously and maintains meticulous oversight of tasks. His strong analytical mindset allows him to assess and optimize processes comprehensively. As a highly responsible team member, he is eager to support and guide the team with his knowledge and takes initiative when necessary. He stands out in the team with his attention to detail, curiosity and enthusiasm for personal growth. He is not afraid to speak up and provide constructive feedback, always aiming for improvement. Berkay thrives in well-defined, systematic settings where clarity, stability and structure prevail, making him a highly efficient and content contributor.''}

\medskip

\cventry{}{Özge Işık}{Product Designer, Emlakjet}{}{}{}
\cvitem{}{``We were colleagues with Berkay at Emlakjet. Berkay is someone who can touch every aspect of the project that we worked on, who respects every idea and has the ability to quickly come up with the solutions to any issue. One of the best aspects of working with him was being able to trust his ideas easily. Being understanding, having a high sense of empathy, and always being open to growth were some of the factors that made our work easier. Hopefully, our paths will cross again; it was very enjoyable to work with you.''}

\medskip

\cventry{}{Hakan Erdoğan}{CEO, Craftgate}{}{}{}
\cvitem{}{``We worked with Berkay during the Navlungo \& Craftgate payment gateway integration process. Berkay is a very proficient, and proactive product guy. We worked with him with great pleasure on matters that require care and diligence, such as payment. I would like to work with him again if possible.''}

\medskip

\cventry{}{Zikriye Ürkmez}{Software Manager, Navlungo}{}{}{}
\cvitem{}{``Berkay has always impressed me with his effective communication skills. His approach to problems and his style of analysis have always been guiding. He is a product owner who always supports his team by taking the initiative. He was always a smiling and kind teammate. Working with him is a great pleasure.''}

\medskip

\cventry{}{Tamay Önal}{Team Lead, Etiya}{}{}{}
\cvitem{}{``Berkay is a sharp innovator, as well as a great friend and a team player and a motivator. We have served together within one of the five largest digital transformation projects in the telco world and observing him achieve results under tough, challenging conditions. I have been impressed by Berkay's full-hearted, innovative approach to his scope. He has always tried (mostly with good success) new ways of doing things, thinking out of the box, and implementing equally creatively while getting the job done. I would---without hesitation---work with him in the future in possible new opportunities, should our roads cross again.''}

\medskip

\cventry{}{Uğur Açıkgöz}{Head of Engineering, MindBehind}{}{}{}
\cvitem{}{``Working together with Berkay was enjoyable and very productive. Thanks to its technical approach to determining business value, business processing, and projecting, we quickly advanced the Turkish Ministry of Health WhatsApp Hotline project, which we worked on during the COVID-19 pandemic closure, and achieved results.''}

\medskip

\cventry{}{Doğa Bekaroğlu}{Team Lead, Turkish Ministry of Health}{}{}{}
\cvitem{}{``During the time I had the opportunity to work with him as a product owner on the project we developed for the General Directorate of Health Promotion; He is one of the most suitable candidates to work for, due to his command of the project and its components, the importance it gives to its details, and its contributions to the progress of the product. In addition, since his undergraduate education is in psychology, his communication with people, the subjects he has developed on software and coding, his technical knowledge and equipment, the synthesis of these components, and the ability to look at events from both sides in analysis and product development stand out in such matters.''}

\end{document}
